Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-01-31 paperMSR.tex

When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code. It may semm at first reasonable to assume that previous modifications of this line or these lines are the cause of the bug; the previous modification is what is called \textit{the previous commit}. But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption. This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}. \grex{Gema, puedes clarificar la frase anterior? No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}

@@

The goal of this paper is to find if the cause of the bug can be attributed to the previous commit. A previous commit will be identified as the cause if the buggy behavior is present at the time it is performed. If the buggy behavior is due to other changes in the software, e.g., due to its evolution or changes elsewhere in the source code base, the previous commit should not be considered as the cause of a bug.

To achieve our goal, this paper attempts to address the following research questions:

\begin{itemize}
    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
    %\item RQ1:     How can we know that a change was done to fix a bug in the source code? How can we identify them?
     \item \gema{RQ1: How we can identify a change done to fix a bug inserted in the code source? Que tal esta forma de plantear la RQ1? Esta pregunta se refiere a como podemos diferenciar los bug reports de los otros pero realizada desde el punto de vista del comit previo }
     \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
    %\item RQ2:  How often is the bug caused in the previous commit?
     \item RQ2: How often is the previous commit the cause of the bug?
\end{itemize}

@@

With this paper we try to shed some ligth on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug. Thus, our idea is based on the thought that some modifications or additions into the code source don't introduce any bug in the software. Our results could lead to think that all the articles based on this assumption are not using the best data in their results.On the other hand, this could be very useful in future research deleting this previous commits from the cause of a bug in their studies and could help developers understanding the bug seeding process. \grex{reescribir este parrafo para que quede mas claro.}

@@

@@

From the experience of analysing a small number of tickets, we agreed on following four criteria:

\begin{enumerate}
    \item When the ticket title described the program as not working as expected, our criteria indicated that it was a bug report. 
    \item When the title described optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket title described that updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected. \grex{no se si esto es lo que querias decir}

%    Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use. When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails. \grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}
\end{enumerate}

@@

The next part is focused on analyzing the previous commit exclusively in the \textit{Bug Report} group to identify which line contained the bug and why the software failed, keeping in mind the context of the project.

\grex{Este parrafo deberia decir lo mismo que el anterior. Si es asi, borremos el anterior}
In this second part, our work was focused on analyzing the previous commit exclusively for those tickets classified in the \textit{Bug Report} group. Therefore we had to locate the line that contained the bug, inquire the reason of the software failure, and gathering additional information on the context of the project.

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit. This way, we can be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug. \grex{Gema, puedes aclarar este parrafo? Que es el "parent" commit? Es lo mismo que el previous commit? Es la primera vez que hablamos de el. Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}

@@

We classify a total of 459 tickets using the tool, resulting in 918 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}. Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.

@@

%\grex{Tiene sentido añadir porcentajes, como he hecho a la columna de Total?}

@@

\grex{Tiene sentido anadir numeros absolutos, como he hecho a la columna de Total en la Tabla 3?}

@@

\grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}

@@

In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} as bug reports and their previous commits.
The possible outcome of the analysis was one of the following three options:

@@

This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug. It may happen that in the previous commit lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced. Thus, the cause could be found in a single previous commit, in many or even in none. \grex{Todavia no esta del todo claro... yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo. Ademas, nos lo podemos permitir; tenemos espacio.}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code. \grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

@@

If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit. As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure. For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not. \grex{Pon ejemplos, a ser posible reales, de esto, porfa.}

\grex{No me queda claro que quieres decir con mas de un identificador previo}

\grex{Para los 58 bugs que tenian mas de un identificador previo hay 179 commits. Bien. Dices que 86 causaron el bug, 82 no y en 11 no se ha podido determinar. Lo que no veo es por que no agruampos estos datos segun los 58 bugs}

@@

We also studied the distribution of the number of previous commits for each bug. As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits. \grex{the number of commits that can be considered as previous is 1, followed by 2 commits. No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo? Que utilidad tiene?}

@@

Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them introduced the bug in the code source. Even if several previous commits are involved, it may be the case that none, only one or all of them is the cause of the bug. \grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}
Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug. If we look at bugs that had two previous commits, in 4 cases both commits were the cause, in 9 cases only one of them was the cause and in another 4 cases non of them could be determined as the cause.

\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}

@@

A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug. Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa? En castellano si quieres}

>>>>

When a failure is found in the behavior of a software, the developers try to fix it locating and modifying the source code line(s) that are reponsible for the wrong behaviour in the source code. It may semm at first reasonable to assume that previous modifications of this line or these lines are the cause of the bug; the previous modification is what is called \textit{the previous commit}. But in fact, to find when and where a bug was introduced in the source code is not a trivial task, and by far more complex than this assumption. This has largely been ignored in many of the bug-fix literature, mainly because the data related to the origin of a bug is embedded in the evolution of the software~\cite{sinha2010buginnings}, meaning that when someone fixes a bug they don't take into consideration the context and the history behind of the project and you cannot have access into this information easily. \grex{Gema, puedes clarificar la frase anterior? No me ha quedado muy claro que querias decir con lo de embedded in the evolution of the software; quizas habria que poner un ejemplo.}\gema{No se si asi queda mas claro, la idea de embebed la saque del articulo y por lo que entendi con embebed se referia a que no hay ningun log o nada donde los desarrolladores expliquen porque se ha producido un error desde un punto de vista mas historico, que la informacion sobre el error se encuentra embebida en la historia y la evolucion del propio proyecto, no creo que pueda sacar ningun ejemplo }

@@

\grex{poner el siguiente parrafo bien}
\gema{podemos eliminar el siguiente parrafo porque en realidad lo que qería decir aquí es la contribucion del paper y si la pongo luego puedo eliminar este parrafo}
The goal of this paper is to find if the cause of the bug can be assigned to the previous commit, understanding that at the time when the previous commit is introduced not all times the code analyzed was so easy as the code showed in Figures~\ref{fig:1} and~\ref{fig:3}. So the principal aim of this paper to find the responsible of the bug is to know if the previous commits contained buggy code at the moment in which were added/modified or, another change in the software, related to the update of the software and its evolution, caused the bug.

In detail, in this paper we attempt to address the following research question regarding who introduced the bug in the source code:

\grex{rephrase RQs}
\begin{itemize}
    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?
     \item \grex{RQ1: How many tickets in the issue tracking system are (real) bug reports?}
     \item \gema{ Me parece bien la pregunta anterior pero queria focalizarla mas desde el punto de vista del commit previo, para que se adapte mas a la idea del articulo ya que en realidad es algo que se debe hacer pero no tiene mucho que ver con encontrar el causante del bug reports, yo había pensado algo como: How we can identify a change done to fix a bug inserted in the code source? }
    %\item RQ2:  How often is the bug caused in the previous commit?
     \item RQ2: How often is the previous commit the cause of the bug?
\end{itemize}

@@

\grex{Aqui deberiamos poner la contribucion de nuestro articulo al estado del arte.}
The goal of this paper is to shed some ligths on how and when the bug was inserted into the source code, showing different empirical results from the the current assumption about the bug was originated in the previous modifications of the lines involved in the fix bug. Thus, our idea is based on the thought that some changes into the code source don't introduce any bug in the software, due to at the moment in which this lines were written, the code wasn't buggy. Finally, our results could lead to think that all the articles based on this assumption are not using the best data in their approach and as a result they can improve their results with our idea. On the other hand, this could be very useful in future researchs, could help developers understanding the bug seeding process.

@@

The SZZ algorithm (and its \emph{successors}) have been widely used in the research community.
Williams et al. revisited the SZZ algorithm to track bug-inducing changes and identify types of changes~\cite{williams2008szz}. Yang et al. applied SZZ to find what kind of bug-inducing changes are likely to become a great threat after being mared as bug-fix changes
Finally, some bug prediction algorithms are based on SZZ; Kim et al. showed how to classify file changes as buggy or clean using change information features and sour code terms~\cite{kim2008classifying}.

\grex{maybe talk about my paper with dmg and ahmed, where bugs could be found elsewhere~\cite{german2009change}. There the talk is precisely about those bugs whose origina are elsewhere. Title of the paper: \emph{Change impact graphs: Determining the impact of prior codechanges}}\gema{me parece bien, no lo he leido pero nadie mejor que tu para resumirlo en esta seccion}

@@

From the experience of analysing a small number of tickets, we agreed on following four criteria: 
\begin{enumerate}

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considerated as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected. \grex{no se si esto es lo que querias decir}\gema{si, es eso lo que queria decir}

%    Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use. When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails. \grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}

\end{enumerate}

@@

In this second part, our work was focused on analyzing the previous commit exclusively for those tickets classified in the \textit{Bug Report} group. Therefore we had to locate the line that contained the bug, inquire the reason of the software failure, and gathering additional information on the context of the project.

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added,inserted or modified in the previous commit, we refered to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file. We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, is a false positive where the previous commit didn't cause the bug. \grex{Gema, puedes aclarar este parrafo? Que es el "parent" commit? Es lo mismo que el previous commit? Es la primera vez que hablamos de el. Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se shan cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del pervio para saber que en realidad en ese momento se produjo el cambio. En el gerrit nos dan esa info como se puede ver en \ref{fig:parent}}
\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\label{fig:patent}       % Give a unique label
\end{figure}

@@

We classify a total of 459 tickets using the tool, resulting in 917 reviews\grex{Mirando la Tabla 2, veo que las revisiones suman 917, no 918!}.\gema{Es cierto, son 917} Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits.

@@

%\grex{Tiene sentido añadir porcentajes, como he hecho a la columna de Total?}
%26-56 hours

@@

After this, we can answer the first research question because at this moment we have all the data necessary and all the knowleadge to can distinguish bug reports from others reports.

\grex{Tiene sentido anadir numeros absolutos, como he hecho a la columna de Total en la Tabla 3?}
\gema{Si, tiene sentido}

@@

\grex{Molaria hablar de cuanto tiempo ha llevado realizar esta etapa de clasificacion por cada uno de los investigadores (o sea, sin contar el desarrollo de herramienta y conseguir y cargar los datos de bugs y demas en la base de datos)}
\gema{El problema es que no hemos medido el tiempo, he hablado con ellos y me dicen que de media de 5 a 10 minutos por ticket, a mi me llevo unos 5 minutos de media, por que ya estaba mas acostumbrada, pero de todas formas se podría medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?}

@@

In this stage we analyzed the 189 tickets classified \grex{Pero no eran 209?} \gema{deberian ser 209 pero me han quedado 20 bugs report por analizar, si tengo tiempo cuando llegue a casa lo hago y anado los numeros} as bug reports and their previous commits.
The possible outcome of the analysis was one of the following three options:

@@

This analysis takes into account that the bug could have been inserted in many lines that belong to many different previous commits, but in fact, not all of them could cause the bug. It may happen that in the previous commit, lines have been copied from further previous commits, comments may have been modified or blank spaces/lines have been introduced. Thus, the cause could be found in a single previous commit, in many or even in none. \grex{Todavia no esta del todo claro... yo creo que esto merece un ejemplo - incluso con codigo real, tal y como hemos hecho al principio del articulo. Ademas, nos lo podemos permitir; tenemos espacio.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}

%\begin{figure}[ht]
%\centering
%\includegraphics[height=12cm]{manylines.png}
%\caption{Screenshot of the tool used to classify the tickets.}
%\label{fig:screenshot}       % Give a unique label
%\end{figure}

@@

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 were identified as not beign the cause. We were unable to decide in 42 cases, as only lines had been added or due to our limited knowleadge about the code. \grex{Gema, puedes poner un ejemplo de estas dos cosas? Uno de solo added lines y otro de limited knowledge. Si el ejemplo es verdadero, mejor.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}
We discarded 40 more because they were false positives (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file.

@@

If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit, whereas 58 had more than one previous commit. As can be seen from Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, and 30 not caused the failure. For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not. \grex{Pon ejemplos, a ser posible reales, de esto, porfa.}\gema{perfecto, ahora busco un ejemplo y lo anado abajo}

\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}

\grex{Para los 58 bugs que tenian mas de un identificador previo hay 179 commits. Bien. Dices que 86 causaron el bug, 82 no y en 11 no se ha podido determinar. Lo que no veo es por que no agruampos estos datos segun los 58 bugs}\gema{Esos datos estan agrupados en la tabla 7, el fin de esta tabla era mostrar que cuando hay un solo comit previo el numero de no causantes del error es menor que cuando hay mas de un commit previo}

@@

We also studied the distribution of the number of previous commits for each bug. As shown in Table~\ref{tab:secondStage2}, the number of commits that can be considered as previous is 1, followed by 2 commits. \grex{the number of commits that can be considered as previous is 1, followed by 2 commits. No se que queremos decir} \grex{Tenemos que responder a estas dos preguntas todavia: Por que es interesante hacer lo que se comenta en este parrafo? Que utilidad tiene?}\gema{Creo que era interesante saber como se distribuyen los causantes de los bugs en cada projecto y cuantos commits previos presentan los bugs report en cada projecto analizado, ademas cuantos mas commits previos, en ocasiones, es muy dificil saber quien es el responsable por tanto pense que podria haber algun patron en relacion con el numero de commits previos y cuantos de ellos son responsables, pero parece que esto no ocurre con la muestra que hemos analizado.}

@@

Finally, we were interested in analyzing, for those cases where more than one previous commit exist, how many of them introduced the bug in the code source. Even if several previous commits are involved, it may be the case that none, only one or all of them is the cause of the bug. \grex{Cuando hay 3 previous commits, no podria darse el caso de 2 de ellos responsables?}\gema{si, eso sucede y eso casos se encuentran dentro de al menos un responsable, (at least one responsible)}
Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug. If we look at bugs that had two previous commits, in 4 cases both commits were the cause, in 9 cases only one of them was the cause and in another 4 cases non of them could be determined as the cause.

\grex{Entiendo el resultado del parrafo anterior, pero me falta una explicacion de por que esto es interesante y para que puede servir.}\gema{Para tener una idea de como se distribuyen los causantes del error, podría eliminar las tablas si en realidad no las encuentras funcionales y no aportan informacion. }

@@

A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug. Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa? En castellano si quieres}
\gema{Si, la idea es realizar el mismo estudio pero con otro projecto que no sea OpenStack, porque en realidad OpenStack esta evolucionando continuamente. Y para poder demostrar que en realidad la idea se cumple en todos los projectos, deberiamos analizar un projecto que sea mas 'estable' y en el que la API no se este cambiando continuamente }
